\documentclass[11pt, a4paper]{moderncv}

% --- MODERNCV THEME ---
\moderncvstyle{classic} 
\moderncvcolor{orange} 

% --- PAGE MARGINS ---
\usepackage[a4paper, scale=0.82]{geometry}

% --- PERSONAL DATA ---
\name{Mitul}{Shah} % Placeholder - replace 'Your Name'
\title{Tech Lead - Backend}
\phone[mobile]{+91 88665 62772} % Placeholder
\email{er.mitulshah@gmail.com} % Placeholder
\homepage{https://shahmitul.github.io/}
\social[linkedin]{https://www.linkedin.com/in/ermitulshah/} % Placeholder
\address{Ahmedabad, Gujarat, India}{}{}{} % Removed full street address for privacy

% --- DOCUMENT ---
\begin{document}

\makecvtitle

% --- PROFESSIONAL SUMMARY ---
\section{Executive Summary}
Results-driven Tech Lead with 14+ years of expertise, including over 10 years in fast-paced, product-based startup industries. Proven leader in architecting and scaling Python applications, building and managing full-stack teams to deliver robust platforms from concept to production. Deep technical proficiency in Django, Flask, and the AWS stack, combined with a strategic mindset for designing scalable architectures, ensuring application security, and optimizing database performance (Redis, Celery) to translate complex business goals into high-availability, cost-effective solutions.

% --- TECHNICAL SKILLS ---
\section{Technical Skills}
\cvitem{Languages}{Python, SQL, JavaScript, HTML/CSS}
\smallskip
\cvitem{Frameworks}{Django, Fast API, Django Rest Framework (DRF), Flask, Celery}
\smallskip
\cvitem{Databases}{Postgres, MySQL, Redis, AWS RedShift, AWS DynamoDB}
\smallskip
\cvitem{Cloud \& DevOps}{AWS (EC2, S3, ECS, Fargate, Lambda, SQS, RDS, API Gateway, CloudWatch), Docker, Linux, Swagger, RabbitMQ}
\smallskip
\cvitem{Data \& Libraries}{Pandas, NumPy, NLTK, Text Mining, Sqlalchemy}
\smallskip
\cvitem{Core Expertise}{System Architecture \& Scaling, Database Optimization, Application Security, Agile Methodologies}

% --- PROFESSIONAL EXPERIENCE ---
\section{Professional Experience}

\cventry{Apr 2021 -- Present}{\textbf{Tech Lead}}{\textbf{MoveEasy (Acq. by AppFolio)}}{\textit{Product-Based Startup}}{\textit{Remote - USA}}{
\begin{itemize}%
    \item Solely architected and built the entire greenfield backend for a comprehensive CRM platform (Django Rest API, Postgres) from the ground up.
    \item Scaled the platform to support over 0.5M realtors, 3,000+ daily calls, and 10,000+ daily orders, demonstrating high reliability and performance.
    \item Subsequently managed a full-stack team (Python/Django, JavaScript, QA) to expand platform features, overseeing the project lifecycle and code reviews.
    \item Engineered the platform to manage complex order funnels for 15+ services and 300+ providers, including scalable database design and custom API development.
    \item Optimized platform performance and database queries, leading to a 30\% reduction in API response times and improving overall user experience.
    \item Built and integrated automated commission calculation modules and key performance reporting dashboards, providing critical insights for management.
    \item \textbf{Tech Stack:} \textit{Python, Django, Rest API, RabbitMQ, Postgres, AWS Services, Pandas, JavaScript, HTML}
\end{itemize}
}

\bigskip
\cventry{Aug 2017 -- Mar 2021}{\textbf{Tech Lead}}{\textbf{Coverfox Insurance}}{\textit{Product-Based Startup}}{\textit{Mumbai, India}}{
\begin{itemize}%
    \item Led the Motor Insurance vertical, managing all technical operations, infrastructure, and integrations with 23+ insurance partners.
    \item Orchestrated the development of a new Group Insurance platform from concept to production, utilizing Python, Docker, and AWS.
    \item Drove initiatives in code optimization and infrastructure scaling (AWS ECS/Fargate), directly contributing to a 20\% reduction in operational costs.
    \item Translated complex business requirements into scalable technical solutions, designing systems to handle custom discount rates for new partners, dealers, and agents.
    \item Enforced high code quality standards through rigorous peer reviews and implemented code optimization strategies to improve platform robustness and performance.
    \item Spearheaded the creation of key modules, including policy renewals, instant renewals, and third-party website integrations.
    \item \textbf{Tech Stack:} \textit{Python 3, Django, Flask, DRF, Docker, Celery, Redis, Sqlalchemy, AWS (ECS, Fargate, Lambda, SQS, RDS, CloudWatch, S3)}
\end{itemize}
}

\bigskip
\cventry{Jun 2015 -- Aug 2017}{\textbf{Senior Python Developer}}{\textbf{EXL Services}}{\textit{}}{\textit{Ahmedabad, India}}{
\begin{itemize}%
    \item Delivered data-driven analytics tools that provided actionable insights for clients, directly influencing their marketing spend and business strategies.
    \item Developed and supported multiple data-driven projects for enterprise clients, including Nordstrom and major financial institutions.
    \item \textbf{Marketing Analytics:} Built a campaign analytics dashboard (Flask, EC2, RedShift) to calculate and visualize metrics for Facebook and Taboola. Developed data-cleaning EMR processes for user behavior tracking.
    \item \textbf{Forecasting:} For Nordstrom, developed Python processes for Click-Through Rate (CTR) benchmarking and forecasting site traffic, orders, and demand.
    \item \textbf{NLP/Sentiment Analysis:} Engineered a sentiment analysis tool using NLTK for text summarization, performing entity recognition, POS-tagging, and categorization on a 200,000+ word dictionary.
    \item \textbf{FinTech Platform:} Led development of 'Meta Funding,' a web platform (Django) connecting lenders and small businesses, integrating QuickBooks API for financial analysis.
    \item \textbf{BI Reporting:} Developed a performance metrics platform (Django, MySQL) for a credit union to analyze loan portfolio performance.
\end{itemize}
}

\bigskip
\cventry{Sep 2012 -- May 2015}{\textbf{Python/PHP Developer}}{\textbf{Simform Solution}}{\textit{}}{\textit{Ahmedabad, India}}{
\begin{itemize}%
    \item Developed and maintained full-stack web applications for multiple clients, utilizing Python (Django) and PHP for backend logic.
    \item Rapidly progressed to a senior role, successfully managing client relationships and delivering projects that met and exceeded business objectives.
    \item Promoted from Junior to Senior Developer, taking on increased responsibility for project architecture, management, and direct client communication.
\end{itemize}
}

% --- EDUCATION ---
\section{Education}
\cventry{2008 -- 2012}{\textbf{Bachelor of Engineering, Information Technology}}
{\textbf{Gujarat Technological University}}{\textit{}}{\textit{Ahmedabad, India}}{}{}
\end{document}
